{\bf A Review on Recent Advances in Unsupervised Relation Extraction} \\ \it Term Paper for Recent Advances on Semantics \\ supervised by Prof.Dr.Pinkal

### 2013-07-21 term-paper/paper.tex
Modified: USP model desc

   Having a corpus of sentences in natural language, USP %???\cite{domingosPoon}
    will induce such a lexicon and will also extract a formal representation for each sentence. In the next 
    subsection we will review the necessary steps toward this goal.
\subsection{Model Description}
\label{ch:model}

>>>>

   Having a corpus of sentences in natural language, USP %???\cite{domingosPoon}
    will induce such a lexicon and will also extract a formal representation for each sentence. In the next 
    subsection we will review the necessary steps toward this goal.
\subsection{Model Description}
\label{ch:model}
In this section we will first identify the three key ideas that the model is built upon them and then 
we will describe the necessary steps toward unsupervised semanitc parsing.

Three observations are made by the authors which is crucial to understand the model assumptions:

\begin{enumerate}
  \item Different syntactic variations of predicates and constants can be clustered together to express
   a same meaning. This can be learned from a raw corpus, in contrast to supervised methods which use meaning annotation of text.
   \item Not only fixed elements in a relation can be clustered together but also arbitrary forms with same sub-forms to co-occured forms 
   can be put in a cluster. In this way the meaning compisiton will be learned through clustering of the forms.
   \item Learning syntax and semantics jointly is a complex problem. Authors have shown that translating a syntactic analyses
   to semantic parse has superior performance over joint learning of syntax and semantics. In this way, a model can be built on the shoulder
   of state-of-the-art syntactic parsers.

\end{enumerate}

Based on these assumptions, they propose a method to model joint probabibility of the dependency tree
and its meaning representation. Markov Logic Networks (MLN) ??? is used to represent the meaning of a sentence.
For each sentence we will have an undirected graphical model (Markov network) which each nodes corresponds to atoms
and cliques correspond to first-order clauses. The best meaning representation is the one which 
maximizes the probability of the observed dependency. %???cite{Titov}
These are the major steps of the USP system:
\begin{description}
  \item[Dependency Parsing] \hfill \\
  the authors believe that dependency parsing is a better starting point that phrase-structure parsing, since it expresses
   the relation-argument structure at the lexical level. They have used Minipar ??? to make the results more comparable with previous
   methods, e.g. DIRT.
  \item[Converting Dependency Trees into Quasi-Logical Forms] \hfill \\
  Extracting lambda forms and atoms (lexical entries) is done by a deterministic procedure. 
  Arguments of a dependency path will be converted to atoms, their predicate consists of the lemma and their part-of-speech tags.
  Each edge from the head to arguments will be a predicate labeled as type of the dependency path.
  This predicate together with two lambda function for each argument form a QLF. In this QLF, only one constant can be presented.

  \item[Clustering Lambda-Forms] \hfill \\
  It starts from atom levels and cluster them based on their relation, then it recursively clusters larger formula
  based on their subformula lambda forms. The composition of meaning of any formula can be obtained by applying
  \emph{lambda reduction} and substituting constants with lambda variables. At the end we will have a clustering
  of lambda forms which each cluster contains a set of semantically equivalent lambda forms. this solves
   the problem of having different syntactic realizations with a same meaning.

  \item[Creating a Markov Logic Network] \hfill \\
  Each atom can be modeled as a node and each first-order clause can be modeled as a feature. This is still not a complete Markov Logical
  Network since this model needs a weighting for features.Thus, the weight of feature is defined as a weight of
  its corredpandant clause. A log-linear distibution $$ P(x) = \frac{1}{Z}\exp{\Sigma_i{(w_i n_i (x))}} $$is used to model the probability of each clique (configuration of nodes and features).

  \item[Learning the weights of MLN] \hfill \\
  \item[Finding the Best Semantic Parse] \hfill \\
  A semantic parse is a partition of atoms of a QLF, assignment of its head and argument form to a cluster. 
  This can be seen as a structre prediction problem. Given the described MLN and its paramters, inference can
   be done by finding a Maximum A Posterior solution. An exact solution needs a summing over all possible syntactic realizations and
   possible dependency parses, therefor a greedy algorithm to search for a good solution is proposed 
   by the authors.   
\end{description}
